---
title: "Keras Tutorial"
author: "Miguel Conde"
date: "24 de abril de 2017"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.align = "center")
```

[R Interface to the Keras Deep Learning Library](https://cran.r-project.org/web/packages/kerasR/vignettes/introduction.html)
[Keras: Deep Learning library for Theano and TensorFlow](https://keras.io/)

Keras is a high-level neural networks API, written in Python and capable of running on top of either [TensorFlow](https://github.com/tensorflow/tensorflow) or [Theano](https://github.com/Theano/Theano). It was developed with a focus on enabling fast experimentation. Being able to go from idea to result with the least possible delay is key to doing good research.

Use Keras if you need a deep learning library that:

* Allows for easy and fast prototyping (through user friendliness, modularity, and extensibility).
* Supports both convolutional networks and recurrent networks, as well as combinations of the two.
* Runs seamlessly on CPU and GPU.

Keras provides a language for building neural networks as connections of general purpose layers. 

NN tutorials:

* [Hacker’s guide to Neural Networks](http://karpathy.github.io/neuralnets/)
* [Neural Networks and Deep Learning](http://neuralnetworksanddeeplearning.com/)
* [Understanding LSTM Networks](http://colah.github.io/posts/2015-08-Understanding-LSTMs/)
* [A Beginner’s Guide to Recurrent Networks and LSTMs](https://deeplearning4j.org/lstm)

## Example 1: Boston Housing Data

Build an empty Sequential model.
```{r}
library(reticulate)
use_condaenv("tensorflow", required = TRUE)
py_discover_config(required_module = "keras")

```

```{r}

Sys.which("python")
```

```{r}
library(kerasR)
mod <- Sequential()
```

